CPSC 504 Project Update \vspace{4 cm}

### 2015-02-28 Project_Update/Update.tex
Phase II write-up.

\subsection{Extraction, Transformation, and Loading (ETL)}
Extraction, transformation, and loading (ETL) \cite{vassiliadis2009extraction}[and the red book] is the process of taking data from one source, changing it, and then putting it into a data warehouse. Although this is not exactly what we are doing, we can still examine how it is done to figure out how to best track the changes made to the data. One of the biggest problems we can foresee for our project is how we can track the various changes made to our data once the user has pulled a copy of the data to his/her interface. We believe that we can use some of the ETL principles to guide how we can best do this process.

>>>>

\subsection{Extraction, Transformation, and Loading (ETL)}
Extraction, transformation, and loading (ETL) \cite{vassiliadis2009extraction} is the process of taking data from one source, changing it, and then putting it into a data warehouse. Although this is not exactly what we are doing, we can still examine how it is done to figure out how to best track the changes made to the data. One of the biggest problems we can foresee for our project is how we can track the various changes made to our data once the user has pulled a copy of the data to his/her interface. We believe that we can use some of the ETL principles to guide how we can best do this process.
